---
title: "Kaggle Housing Prices"
author: "Michael Sebald"
date: "12 März 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
suppressPackageStartupMessages(library(data.table))
suppressPackageStartupMessages(library(magrittr))
```

## Training Set
### Information from the data description
```{r}
factor_vars <- c("MSSubClass", "MSZoning", "Street", "Alley", "LotShape", 
                 "LandContour", "Utilities", "LotConfig", "LandSlope",
                 "Neighborhood", "Condition1", "Condition2", "BldgType",
                 "HouseStyle", "RoofStyle", "RoofMatl", "Exterior1st",
                 "Exterior2nd", "MasVnrType", "ExterQual", "ExterCond", 
                 "Foundation", "BsmtQual", "BsmtCond", "BsmtExposure", 
                 "BsmtFinType1", "BsmtFinType2", "Heating", "HeatingQC",
                 "CentralAir", "Electrical", "KitchenQual", "Functional",
                 "FireplaceQu", "GarageType", "GarageFinish", "GarageQual",
                 "GarageCond", "PavedDrive", "PoolQC", "Fence", "MiscFeature", 
                 "SaleType", "SaleCondition")
                 
factor_vars_2 <- c("OverallQual", "OverallCond")
```

### Input
```{r}
train <- read.csv("train.csv")
dim(train)
```

### Number of NAs 
```{r}
sapply(train, function(x) {sum(is.na(x))})
```

### Convert into factors
```{r}
train[factor_vars] <- lapply(train[factor_vars], factor)
str(train)
```
### Replacing NAs with proper values
```{r}
vals_fix_nas <- c("Alley", "BsmtQual", "BsmtCond", "BsmtExposure", 
                  "BsmtExposure", "BsmtFinType1", "BsmtFinType2",
                  "FireplaceQu", "GarageType", "GarageFinish", "GarageQual",
                  "GarageCond", "PoolQC", "Fence", "MiscFeature")

for (i in 1:length(vals_fix_nas)) {
  levels(train[, vals_fix_nas[i]]) <- c(levels(train[, vals_fix_nas[i]]), "None")
  train[is.na(train[vals_fix_nas[i]]), vals_fix_nas[i]] <- "None"
}
```

### Adjust levels - to be done - not even sure this makes sense
```{r}
levels(train$BsmtQual) <- c(10, 4, 8, 6, NA, 2)
levels(train$BsmtCond) <- c()
levels(train$FireplaceQu)
levels(train$GarageQual)
levels(train$GarageCond)

levels(train$PoolQC)


levels(train$ExterQual)
levels(train$ExterCond)

levels(train$HeatingQC) <- c(8, 2, 6, 0, 4)
train$HeatingQC <- as.numeric(train$HeatingQC)

levels(train$KitchenQual) <- c(8, 2, 6, 4, 0)
train$KitchenQual <- as.numeric(train$KitchenQual)
```

### Number of unique values
```{r}
sapply(train, function(x) {length(unique(x))})
```


### Questions, observations, lessons learned

* several numeric variables are actually categorial dimensions, so simply using strings_as_factors doesn't help
* also, some numeric variables like _OverallQual_ are categorial but their numeric value seems to usable as is, so should we leave them as numeric?
* not all possible factor levels exist in the training data set
* several categorial variables indicate a "quality level" -> convert them into numeric values?
* some dimensions occur twice, in two different columns. How to treat them?
* which variables should be transformed?
* how do we treat dependant variables, e.g. BsmtFinType1 and BsmtFinSF1?
* how do we consider variables which occur very seldom? Only 7 properties have a pool
